Spatial Reasoning and Statistical Graphics

### 2014-10-16 Paper/Draft1/TestingVisualAptitude.Rnw
Nicer t-test tables - getting rid of raw R output

<<t.test.sex, echo=T, comment="|">>=
t.test(ans.summary$lineup[ans.summary$sex=="m"], ans.summary$lineup[ans.summary$sex=="f"])
@
<<t.test.calculus, echo=T, comment="|">>=
t.test(ans.summary$lineup[ans.summary$calc_1=="y"], ans.summary$lineup[ans.summary$calc_1=="n"])
@
<<lm.vid.games, echo=T, comment="|">>=
ans.summary$vidgame_hrs_factor_new <- factor(ans.summary$vidgame_hrs_factor, ordered=FALSE)
summary(lm(data=ans.summary, lineup~vidgame_hrs_factor_new))
# summary(lm(data=ans.summary, lineup~vidgame_hrs))
@
<<lm.all, echo=T, comment="|">>=
summary(lm(data=ans.summary, lineup~sex+calc_1+vidgame_hrs_factor_new))
@
All results and data shown here are done in accordance with IRB \# 13-581.

@@

\section*{Appendix}
T-tests of results for Hillary and Stephanie: 
<<ttest, echo=T, include=T>>=
t.test(ans.summary$card_rot[1:18], ans.summary$card_rot[-c(1:18)])
t.test(ans.summary$folding[1:18], ans.summary$folding[-c(1:18)])
t.test(ans.summary$lineup[1:18], ans.summary$lineup[-c(1:18)])
t.test(ans.summary$vis_search[1:18], ans.summary$vis_search[-c(1:18)])
@

>>>>

<<ttests.categ, echo=F, results='asis'>>=
tmp <- dlply(lineup.summary.categorical, .(variable), function(df){
    tmp <- anova(lm(lineup~factor(value, ordered=F), data=df))
    coefs <- as.data.frame(tmp)[1,]
    coefs$level <- gsub("factor(value, ordered = F)", unique(df$variable), rownames(coefs), fixed=T)
    rownames(coefs) <- NULL
    coefs <- coefs[,c(6, 1:5)]
    names(coefs) <- c("Variable", "DF", "Sum.of.Squares", "Mean.Squared", "F.value", "p.value")
    coefs
})

tmp <- rbind.fill(tmp)
tmp <- tmp[order(tmp$p.value, decreasing=F),]
library(xtable)
print(xtable(tmp, digits=c(1, 1, 0, 3, 3, 2, 3)), include.rownames=F)
@

All results and data shown here are done in accordance with IRB \# 13-581.

@@

\section*{Appendix}
T-tests of results for Hillary and Stephanie: 
<<ttest, echo=F, include=T, results='asis'>>=
library(xtable)
ans.summary$tester <- c(rep("Hillary", 18), rep("Stephanie", nrow(ans.summary)-18))
card.rotation <- t.test(card_rot~tester, data=ans.summary)
paper.folding <- t.test(folding~tester, data=ans.summary)
fig.class <- t.test(fig_class~tester, data=ans.summary)
lineup <- t.test(lineup~tester, data=ans.summary)

res <- ldply(ans.summary[,c("card_rot", "folding", "fig_class", "lineup")], function(i){
  tmp <- t.test(i~ans.summary$tester)
  data.frame(Hillary = as.numeric(tmp$estimate)[1], Stephanie = as.numeric(tmp$estimate)[2],
             t = tmp$statistic, df=tmp$parameter, p=tmp$p.value, lb = tmp$conf.int[1], ub=tmp$conf.int[2])
})

res$.id <- c("Card Rotation", "Paper Folding", "Figure Classification", "Lineups")
names(res) <- c("Variable", "Mean.Hillary", "Mean.Stephanie", "t", "df", "p-value", "Diff.LB", "Diff.UB")

print(xtable(res), include.rownames = F)
@
